Ethikbumms*\\ {\footnotesize \textsuperscript{*}Mit bisschen Datenschutz bumms} \thanks{Identify applicable funding agency here. If none, delete this.}

### 2022-05-25 draft.tex
add wip abstract and format

\documentclass[12pt,a4paper]{article}
\usepackage[a4paper,top=20mm,bottom=25mm,left=20mm,right=40mm]{geometry}

@@

\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

@@

\newenvironment{somebox}{\par\noindent%
   \begin{minipage}{\linewidth}}
   {\end{minipage}\par\vfill}

\usepackage[onehalfspacing]{setspace}

\begin{document}

\pagenumbering{gobble}
\begin{titlepage}
	\begin{center}
Hochschule Karlsruhe für Technik und Wirtschaft

\vspace{2cm}
\LARGE
\textbf{Ethikbumms}

\vspace{0.5cm}
\Large
Mit bisschen Datenschutz bumms

	\end{center}
\vfill
\large

Jenny Hilgenberg \& Bileam Scheuvens

\vspace{0.5cm}
Betreuer: Neumann \& Stengel

\end{titlepage}
	\newpage

\tableofcontents
	\newpage

\pagenumbering{arabic}
\setcounter{page}{3}

	\newpage
\section{Historical and Technical Introduction}

@@

\subsection{Totalitarian Police State}

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}

@@

@@

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\begin{document}
\pagenumbering{gobble}

\title{Ethikbumms*\\
{\footnotesize \textsuperscript{*}Mit bisschen Datenschutz bumms}
\thanks{Identify applicable funding agency here. If none, delete this.}
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Benedict Bileam Scheuvens}
\IEEEauthorblockA{\textit{Data Science} \\
\textit{Hochschule Karlsruhe für Technik und Wirtschaft}\\
Karlsruhe, Germany \\
scbe1047@h-ka.de}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Jennifer Hilgenberg}
\IEEEauthorblockA{\textit{Data Science} \\
\textit{Hochschule Karlsruhe für Technik und Wirtschaft}\\
Karlsruhe, Germany \\
hije1012@h-ka.de}
}

\maketitle

\begin{abstract}
A few centuries ago, life love and a the universe were a mystery, but driven by deeply rooted human curiosity we are beginning to untangle the mess and understand the foundation that grew consciousness out of thin air. One piece of this puzzle is DesoxyriboNucleic Acid. The genetic material that after being refined by millenia of pure chance and survival holds the blueprint to every living creature on our planet. With growing understanding about its structure and the technological advancements that gave us tools to manipulate it, humanity has set its foot in the doorstep to a world in which DNA is no different than a LEGO brick and nothing is out of reach.
This paper aims to explore aspects of how this applied genetics will impact us in regard to ethics and data privacy. 
Genetic engineering is as much blessing as a curse and must be used with caution, while genome analysis unveils a tremendous amount of information not just about us, but about our relatives as well.
\end{abstract}
\section{Historical and Technical Introduction}

@@
